Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2020-03-31 slides/ExpSlides.tex
1.slides draft before discussion with Jonanthan. need to summarize the results and rewrote the conclusion.

	\begin{itemize}
		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
		\item  $\Gamma$: constraints for the parameter. 
		\item $M_{data}$: data moments
		\item $F$: simulated model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up till each point of the time $t$. 
		\begin{itemize}
			\item unconditional moments, not specific to time
			\item moments selected from average forecast, variance and autocovariance of forecasts, average diagreement, variance and autovariance of disagreement, average uncertainty, etc. 
		\end{itemize}
		\item  $W$: weight matrix, identity matrix for now 
	\end{itemize}
\end{frame}

@@

@@

\begin{frame}{Professionals and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Professionals and SEAR: joint estimation}
	\begin{figure}[ht]
		\label{SE_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR: joint estimates}
	\begin{figure}[ht]
		\label{SE_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{SE parameter estimate}
	\begin{table}
		\centering
		\caption{SMM Estimates of Parameters of SE}
		\label{SMM_Est_SE_Table}
	\begin{tabular}{llllllllllll}
		\hline 
		0     & 1       & 2       & 3       & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
		\hline 
		FEVar & FEATV   &         &         & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.59                       & 0.99       & 0.08         \\
		FEVar & DisgATV & DisgVar &         & 0.27                       & 0.38                       & 1          & 0.11         & 0.2                        & 0.56                       & 0.98       & 0.08         \\
		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08         \\
		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08        \\
		\hline 
	\end{tabular}
	\end{table}
\begin{itemize}
	\item $\lambda$: update rate in SE
\end{itemize}
\end{frame}

\begin{frame}{Professionals and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
		\end{subfigure}
	\end{figure}
	\end{frame}

\begin{frame}{Professionals and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

@@

\begin{frame}{Professionals and SESV}
	\begin{figure}[ht]
		\label{SESV_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

>>>>

	\begin{itemize}
		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni},{de},{seni} \} \times \{ar, sv\}$
		\item  $\Gamma$: constraints for the parameter. 
		\item $M_{data}$: data moments
		\item $F$: simulated model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up till each point of the time $t$. 
		\begin{itemize}
			\item unconditional moments, not specific to time
			\item moments selected from average forecast, variance and autocovariance of forecasts, average diagreement, variance and autovariance of disagreement, average uncertainty, etc. 
		\end{itemize}
		\item  $W$: weight matrix, identity matrix for now 
	\end{itemize}
\end{frame}

@@

\begin{frame}{Scoring card for a theory of expectation formation}
	To look if the parameter and fitness is relatively robust to 
	\begin{enumerate}
		\item use of different moments in estimation
		\item alternative assumption about underlying process 
		\item two-step estimation or joint-estimation 
		\item relatively fit with professionals and households  
	\end{enumerate}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%
\subsubsection{SE}

\begin{frame}{SE parameter estimate}
	\begin{table}
		\centering
		\caption{SMM Estimates of SE}
		\label{SMM_Est_SE_Table}
		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
	\begin{tabular}{lllllllllllll}
		\hline 
		0     & 1       & 2       & 3       &     & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
		\hline 
		FEVar & FEATV   &         &         &     & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.5                        & 0.84       & 0.25         \\
		FEVar & DisgATV & DisgVar &         &     & 0.47                       & 0.38                       & 1          & 0.1          & 0.21                       & 0.54                       & 0.92       & 0.18         \\
		FEVar & FEATV   & DisgVar & DisgATV & Var & 0.47                       & 0.36                       & 1          & 0.08         & 0.21                       & 0.5                        & 0.84       & 0.25       \\
		\hline 
	\end{tabular}
	}
	\end{table}
	\begin{itemize}
		\item $\lambda$: update rate in SE
	\end{itemize}
\end{frame}

\begin{frame}{Professionals and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Professionals and SEAR: joint estimation}
	\begin{figure}[ht]
		\label{SE_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
	\begin{subfigure}[b]{0.2\textwidth}
		\caption{FE/Disg}
		\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
	\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR: joint estimates}
	\begin{figure}[ht]
		\label{SE_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{DE}

\begin{frame}{DE parameter estimate}
	\begin{table}
		\centering
		\caption{SMM Estimates of DE}
		\label{SMM_Est_DE_Table}
		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
		\begin{tabular}{lllllllllllllllllll}
			\hline 
			0  & 1     & 2     & 3    & 4       & 5       & 6   & DE: $\theta_{SPF}$ & DE: $\sigma_{\theta,SPF}$ & DE: $\theta_{SPF}$ & DE: $\sigma_{\theta,SPF}$ & DE: $\rho$ & DE: $\sigma$ & DE: $\theta_{SCE}$ & DE: $\sigma_{\theta,SCE}$ & DE: $\theta_{SCE}$ & DE: $\sigma_{\theta_SCE}$ & DE: $\rho$ & DE: $\sigma$ \\
			\hline 
			FE & FEVar & FEATV &      &         &         &     & -0.23              & 0.22                      & NA                 & NA                        & NA         & NA           & 9.35               & 10.65                     & 0.82               & 0.85                      & 1          & 0            \\
			FE & FEVar & FEATV & Disg & DisgVar & DisgATV &     & -0.26              & 1.41                      & -0.14              & 1.44                      & 0.99       & 0.16         & 8.2                & 9.52                      & 4.79               & 4.59                      & 0.58       & 0.55         \\
			FE & FEVar & FEATV & Disg & DisgVar & DisgATV & Var & -0.24              & 1.43                      & -0.17              & 1.44                      & 0.99       & 0.16         & 4.78               & 3.01                      & NA                 & NA                        & NA         & NA          \\
			\hline 
		\end{tabular}
		}
	\end{table}
	\begin{itemize}
	\item $\theta$: representativeness parameter, $\theta>0$ according to DE. 
	\item $\sigma_\theta$: dispersion of representativeness across population
\end{itemize}
\end{frame}

\begin{frame}{Professionals and DEAR}
	\begin{figure}[ht]
		\label{DE_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Professionals and DEAR: joint estimate}
	\begin{figure}[ht]
		\label{DE_diag_joint_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and DEAR}
	\begin{figure}[ht]
		\label{DE_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and DEAR: joint estimates}
	\begin{figure}[ht]
		\label{DE_diag_joint_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%
\subsubsection{NI}

\begin{frame}{NIAR parameters}
	\begin{table}
		\centering
		\caption{SMM Estimates of NI}
		\label{SMM_Est_NI_Table}
		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
			\begin{tabular}{lllllllllllllllll}
				\hline 
				0     & 1     & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
				\hline 
				FEVar & FEATV &         &         &     & 0.09                      & 2.77                  & 0.093                     & 1.408                 & 0.911      & 0.422        & 3.4                       & 15.4                  & 3.397                     & 15.395                & 0.997      & 0.027        \\
				FEVar & FEATV & DisgVar & DisgATV &     & 0.09                      & 2.77                  & 0.093                     & 1.408                 & 0.911      & 0.422        & 3.4                       & 15.4                  & 3.397                     & 15.395                & 0.997      & 0.027        \\
				FEVar & FEATV & DisgVar & DisgATV & Var & 0.14                      & 3.85                  & 0.133                     & 1.359                 & 0.911      & 0.422        & 4.9                       & 22.4                  & 4.860                     & 22.367                & 0.997      & 0.027       \\
				\hline 
			\end{tabular}
	}
	\end{table}	
	\begin{itemize}
		\item $\sigma_{pb}$: noisiness of public signals in NI
		\item $\sigma_{pr}$: noisiness of private signals in NI
	\end{itemize}
\end{frame}

\begin{frame}{Professionals and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
		\end{subfigure}
	\end{figure}
	\end{frame}

\begin{frame}{Professionals and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
		\end{subfigure}
		\end{figure}
\end{frame}

\begin{frame}{Households and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%
\subsubsection{Hybird of NI and SE}

\begin{frame}{SENIAR parameters}
	\begin{table}
		\centering
		\caption{SMM Estimates of SENI}
		\label{SMM_Est_SENI_Table}
		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
		\begin{tabular}{lllllllllllll}
			\hline 
			0  & 1     & 2     & 3    & 4       & 5       & 6   & SENI: $\lambda$ & SENI: $\sigma_{pb,SPF}$ & SENI: $\sigma_{pr,SPF}$ & SENI: $\lambda$ & SENI: $\sigma_{pb,SCE}$ & SENI: $\sigma_{pr,SCE}$ \\
			\hline 
			FE & FEVar & FEATV &      &         &         &     & 0.64            & 0.16                    & 0                       & 0.19            & 0.2                     & 0.21                    \\
			FE & FEVar & FEATV & Disg & DisgVar & DisgATV &     & 0.62            & 4.77                    & 0.17                    & 0.25            & 0.1                     & 0.35                    \\
			FE & FEVar & FEATV & Disg & DisgVar & DisgATV & Var & 0.62            & 13.7                    & 0.17                   & NA              & NA                      & NA                     \\
			\hline 
		\end{tabular}
		}
	\end{table}	
	\begin{itemize}
		\item $\sigma_{pb}$: noisiness of public signals in NI
		\item $\sigma_{pr}$: noisiness of private signals in NI
	\end{itemize}
\end{frame}

\begin{frame}{Professionals and SENIAR}
	\begin{figure}[ht]
		\label{SENI_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and SENIAR}
	\begin{figure}[ht]
		\label{SENI_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

@@

\subsubsection{SE}

\begin{frame}{SESV parameters}
	\begin{table}
		\centering
		\caption{SMM Estimates of Parameters of SESV}
		\label{SMM_Est_SE_SV_Table}
		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
\begin{tabular}{llllllllll}
	\hline 
	0       & 1       & 2       & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\gamma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\gamma$ \\
	\hline 
	DisgATV & Var     &         &     & 0.3                        & 0.46                       & 2.52         & 0.09                       & 0.09                       & 0.7          \\
	FEATV   & DisgVar & DisgATV &     & 0.3                        & 0.46                       & 2.53         & 0.07                       & 0.07                       & 0.26         \\
	FEATV   & DisgVar & DisgATV & Var & 0.3                        & 0.46                       & 1.26         & 0.07                       & 0.07                       & 0.26        \\
	\hline 
\end{tabular}
		}
		\begin{itemize}
			\item $\lambda$: update rate in SE
				\item $\gamma$: size of the innovation to volatility	
		\end{itemize}
	\end{table}	
\end{frame}

\begin{frame}{Professionals and SESV}
	\begin{figure}[ht]
		\label{SESV_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Professionals and SESV: joint estimates}
	\begin{figure}[ht]
		\label{SESV_diag_joint_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag1.png}
		\end{subfigure}
		\hfill
	\begin{subfigure}[b]{0.2\textwidth}
		\caption{Disg}
		\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag2.png}
	\end{subfigure}
	\end{figure}
\end{frame}
